\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage[english,vietnamese]{babel}
\else
  \usepackage{fontspec}
  \usepackage{polyglossia}
  \setdefaultlanguage{english}
  \setotherlanguage{vietnamese}
  \defaultfontfeatures{Ligatures=TeX}
  \setmainfont{TeX Gyre Termes}
\fi
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{center}
    \textbf{\Huge \scshape Nguyen Duy Khuong} \\ \vspace{1pt}
    \small Technical Architect / Technical Leader \\ \vspace{2pt}
    \small 0902637745 $|$ nguyenromio@gmail.com $|$ github.com/khuongnd60493 $|$ www.linkedin.com/in/romio-nguyen
\end{center}

\vspace{4pt}
\small As a dedicated Technical Architect with experience in building and optimizing software solutions, I am eager to bring my technical expertise and collaborative approach to a forward-thinking organization. My goal is to drive robust, scalable solutions that adapt to future industry trends.

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Information Technology (Planned)}{2026 - Expected 2028}
      {University of Information Technology, VNU-HCM (UIT)}{}
      \resumeItemListStart
        \resumeItem{Planning to pursue a Master's degree in Information Technology. The rigorous program will focus on advanced algorithms, distributed systems, and particularly on Big Data processing to architect and scale enterprise data solutions.}
      \resumeItemListEnd

    \resumeSubheading
      {Bachelor of Information Technology (Honors)}{}
      {University of Science, VNU-HCM (HCMUS)}{}
      \resumeItemListStart
        \resumeItem{Graduated with Honors from the Faculty of Information Technology, one of the most prestigious computer science programs in Vietnam. The rigorous curriculum provided a deep theoretical foundation in Data Structures, Advanced Algorithms, and Systems Architecture. Specialized coursework included Enterprise Software Development, Distributed Databases, and Artificial Intelligence, cultivating a strong engineering mindset for building scalable, high-performance applications.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Certifications}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
        \resumeItem{VSTEP B2 (Level 4) - Van Lang University (2026)}
        \resumeItem{Developing Web Application with Spring Framework - FPT Nanoversity HCM (2017)}
        \resumeItem{Web Developer: MVC 5 (Microsoft Certificate) - Nhat Nghe Centre (2016)}
        \resumeItem{Web Developer: C\#, ASP.Net, SQL Server (Microsoft Certificate) - Nhat Nghe Centre (2016)}
  }}
\end{itemize}

\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Team Leader / Senior Fullstack Developer}{05/2025 - Current}
      {Dcorp Vietnam}{Ho Chi Minh City}
      \resumeItemListStart
        \resumeItem{Architect robust backend services using .NET Core and Java, capable of handling massive daily transaction volumes and high-throughput POS requests.}
        \resumeItem{Oversee the fullstack development of supplementary web portals and mobile applications to provide a seamless operational experience.}
        \resumeItem{Solve complex Big Data challenges, optimizing databases and query performance to process and aggregate large-scale enterprise data efficiently.}
        \resumeItem{Bridge on-premise POS deployments with scalable cloud-native microservices, ensuring continuous data synchronization and high availability.}
        \resumeItem{Successfully maintained system stability and fast response times under extreme peak loads for nationwide restaurant chains.}
        \resumeItem{Streamlined data synchronization between offline terminals and centralized cloud services to support real-time big data analytics.}
      \resumeItemListEnd

    \resumeSubheading
      {Technical Architecture / Technical Leader}{03/2023 - 04/2025}
      {MEDIASTEP}{Ho Chi Minh City}
      \resumeItemListStart
        \resumeItem{Developed strategic technical solutions for F\&B, aligning with Product Owner and client needs.}
        \resumeItem{Led R\&D team of 6 to explore and apply new technologies.}
        \resumeItem{Managed a cross-functional team of >40 engineers to hit critical milestones and ensured high-quality, smooth releases.}
        \resumeItem{Conducted training sessions to raise team skills and led code reviews.}
        \resumeItem{Successfully implemented new technologies to boost performance and reliability.}
        \resumeItem{Improved release quality through technical review governance and cross-functional quality control.}
      \resumeItemListEnd

    \resumeSubheading
      {Senior Fullstack Developer / Leader}{10/2021 - 03/2023}
      {ALTSOURCE VIETNAM}{Ho Chi Minh City}
      \resumeItemListStart
        \resumeItem{Acted as Team Leader and Senior Fullstack Developer across multiple client projects (Brighter Path, My Fertility Health, Arcadia Drilling, Trimet, Pacific Architectural Wood Products).}
        \resumeItem{Designed and implemented fullstack solutions using .NET Core, and React/Vue.}
        \resumeItem{Delivered Brighter Path teaching system for ethnic women.}
        \resumeItem{Successfully delivered the subway camera surveillance system upgrade.}
        \resumeItem{Built and scaled door production process management.}
        \resumeItem{Optimized query and data processing performance to keep systems stable under growing workloads.}
      \resumeItemListEnd

    \resumeSubheading
      {Senior Fullstack Developer / Team Leader}{09/2018 - 10/2021}
      {HANBIRO VIETNAM}{Ho Chi Minh City}
      \resumeItemListStart
        \resumeItem{Led development teams ranging from 2 to 7 members across multiple projects.}
        \resumeItem{Managed the migration of company website from Java (jsp-servlet) to Vuex.}
        \resumeItem{Built Hanbiro HR, Groupware, and CRM Supply Chain Management systems.}
        \resumeItem{Built Hanbiro CRM Call, a call management center using Electron and Reactjs.}
        \resumeItem{Contributed to modernizing legacy modules into a more maintainable and scalable technology stack.}
        \resumeItem{Delivered multiple core internal systems including HR, Groupware, and CRM Supply Chain modules.}
      \resumeItemListEnd

    \resumeSubheading
      {Middle Fullstack Developer}{01/2018 - 09/2018}
      {FPT SOFTWARE}{Ho Chi Minh City}
      \resumeItemListStart
        \resumeItem{Built 'Learning Chinese for Japanese' mobile project.}
        \resumeItem{Developed a medical app for booking appointments and reminding prescriptions.}
        \resumeItem{Successfully delivered the 'Learning Chinese for Japanese' mobile application within project timelines.}
        \resumeItem{Built a medical information app that improved appointment booking and medication reminder workflows.}
        \resumeItem{Collaborated effectively across cross-functional teams to ensure stable mobile releases.}
      \resumeItemListEnd

    \resumeSubheading
      {Middle Fullstack Developer / Team Leader}{02/2015 - 12/2017}
      {VINHDANH COMPANY}{Ho Chi Minh City}
      \resumeItemListStart
        \resumeItem{Led a team of 10 to serve the teaching and learning of English for Vietnamese people.}
        \resumeItem{Led a 10-member team to launch the Riolish product for the English learning market.}
        \resumeItem{Delivered both admin web platform and companion mobile application for operational use.}
        \resumeItem{Supported iterative product improvements that expanded user adoption and service quality.}
      \resumeItemListEnd

    \resumeSubheading
      {Internship Fullstack Developer}{02/2014 - 02/2015}
      {FPT SOFTWARE}{Ho Chi Minh City}
      \resumeItemListStart
        \resumeItem{Collaborator in programming the reading software.}
        \resumeItem{Completed internship contributions successfully on Toshiba's reading application project.}
        \resumeItem{Contributed to core feature implementation of the reading software as part of the engineering team.}
        \resumeItem{Built a strong foundation in software delivery process and teamwork in an enterprise environment.}
      \resumeItemListEnd

    \resumeSubheading
      {Fullstack Developer}{03/2012 - 02/2014}
      {DATASA.NET}{Ho Chi Minh City}
      \resumeItemListStart
        \resumeItem{Built an e-commerce website for computer and mobile products including purchase and admin pages.}
        \resumeItem{Delivered a complete e-commerce website including customer purchase flow and admin management modules.}
        \resumeItem{Implemented business requirements for computer and mobile product sales workflows.}
        \resumeItem{Established early fullstack delivery experience through real production project execution.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Dcorp F\&B Enterprise Ecosystem} $|$ \emph{Team Leader / Senior Fullstack Developer}}{}
          \resumeItemListStart
            \resumeItem{A hybrid (On-premise \& Cloud Microservices) POS and enterprise management ecosystem serving major F\&B chains such as Highland Coffee and Golden Gate, covering order lifecycle, pricing, promotion, loyalty, and centralized operational reporting.}
            \resumeItem{Architected robust backend services in .NET Core and Java to process massive daily transaction volumes.}
            \resumeItem{Engineered reliable Big Data pipelines and synchronized data between offline POS terminals and the cloud.}
            \resumeItem{Designed highly available infrastructure utilizing Redis and Kafka for high-throughput queuing.}
            \resumeItem{At Dcorp Vietnam, this platform ensured uninterrupted operations and real-time analytics for nationwide restaurant chains, supporting high daily concurrency and revenue-critical transactions. The architecture reduced downtime risk, shortened release lead time for franchise features, and improved operational visibility for both store-level and head-office decision making.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Go Food and Beverage Ecosystem (GoF\&B)} $|$ \emph{Technical Architecture Lead}}{}
          \resumeItemListStart
            \resumeItem{A comprehensive strategic technical solution for the F\&B industry, managing orders, POS, kitchen workflows, promotion execution, and multi-branch operations.}
            \resumeItem{Led R\&D for exploring and applying new technologies}
            \resumeItem{Designed highly scalable backend architecture}
            \resumeItem{Managed a cross-functional team of 40+ members}
            \resumeItem{At MEDIASTEP, this ecosystem improved transaction throughput and platform reliability for high-volume F\&B operations. The architecture enabled business teams to launch campaigns faster, manage inventory workflows consistently across multiple storefronts, and reduce release risk during high-traffic business periods.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Brighter Path} $|$ \emph{Team Leader / Senior Fullstack Developer}}{}
          \resumeItemListStart
            \resumeItem{An educational platform designed to empower ethnic women through structured learning paths, accessible web UX, and progress tracking for community-driven training programs.}
            \resumeItem{Developed a responsive learning portal}
            \resumeItem{Integrated secure user management and progress tracking}
            \resumeItem{Built modular content and enrollment flows to support iterative curriculum expansion.}
            \resumeItem{At ALTSOURCE VIETNAM, this platform expanded access to digital education for ethnic women in underserved areas. Strong availability and usability improved learner engagement, while structured learning analytics gave stakeholders clearer evidence for scaling and continued program investment.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{My Fertility Health: Clinic Management} $|$ \emph{Team Leader}}{}
          \resumeItemListStart
            \resumeItem{A clinic management platform supporting appointment operations, care workflows, and treatment data tracking for fertility-focused services.}
            \resumeItem{Designed a scalable service architecture for clinic operations and appointment workflows.}
            \resumeItem{Built API integrations between ReactJS frontend and .NET Core/Golang backend services.}
            \resumeItem{Optimized MS SQL data models and query paths for day-to-day operational tasks.}
            \resumeItem{At ALTSOURCE VIETNAM, this project standardized clinic operational workflows and improved treatment data visibility. The platform stability helped operations teams handle patient volume more effectively during peak periods.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Arcadia Drilling: Process Management System for Water-Related Issues} $|$ \emph{Team Leader}}{}
          \resumeItemListStart
            \resumeItem{A process management system for drilling operations, focused on digitizing water-related incident workflows and cross-role operational coordination.}
            \resumeItem{Designed extensible process architecture for field incident handling scenarios.}
            \resumeItem{Delivered backend services with .NET Core/Golang integrated with ReactJS interfaces.}
            \resumeItem{Implemented centralized operational data flows on MS SQL with Azure infrastructure.}
            \resumeItem{At ALTSOURCE VIETNAM, this project improved consistency in water-related incident handling, reduced response time, and strengthened collaboration across field operation teams.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Pacific Architectural Wood Products: Door Production Process Management} $|$ \emph{Senior Fullstack Developer}}{}
          \resumeItemListStart
            \resumeItem{A production process management system for a wood manufacturing business, focused on door production workflow, progress tracking, and cross-team operational coordination.}
            \resumeItem{Designed business architecture for production workflows and stage-based order status tracking.}
            \resumeItem{Implemented backend services with .NET Core/Golang integrated with Angular admin interfaces.}
            \resumeItem{Optimized operational data storage and query performance on MS SQL within Azure infrastructure.}
            \resumeItem{At ALTSOURCE VIETNAM, this project digitized door manufacturing workflows, improved real-time production visibility, and reduced coordination delays across factory operation teams.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Trimet Subway Camera Surveillance} $|$ \emph{Team Leader / Senior Fullstack Developer}}{}
          \resumeItemListStart
            \resumeItem{A modernization project for subway camera surveillance publishing and monitoring, focused on stream stability, visibility, and operational responsiveness.}
            \resumeItem{Optimized video streaming and data publishing pipelines}
            \resumeItem{Enhanced system security and monitoring capabilities}
            \resumeItem{Refined incident-oriented telemetry and operational dashboards for support teams.}
            \resumeItem{At ALTSOURCE VIETNAM, this project delivered a reliable real-time surveillance workflow for subway operations with stronger monitoring and security controls. Stream and publishing optimizations reduced buffering, improved operational response during peak usage, and increased confidence for transit operations teams.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Hanbiro CRM Call: Call Management Center} $|$ \emph{Leader Fullstack Developer}}{}
          \resumeItemListStart
            \resumeItem{A CRM Call platform for call-center operations, customer-care workflow handling, and support team coordination.}
            \resumeItem{Designed real-time call handling and support status tracking architecture.}
            \resumeItem{Built desktop workflow application with Electron, Reactjs, and Node.}
            \resumeItem{Optimized operational data storage and query flows on MySQL.}
            \resumeItem{At HANBIRO VIETNAM, this project helped call-center teams centralize call operations and improve service-response quality through better workflow visibility.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Asein: Migration from JSP/Servlet (Java) to Vuex} $|$ \emph{Leader Fullstack Developer}}{}
          \resumeItemListStart
            \resumeItem{A front-end modernization project for Asein's company website, migrating from legacy JSP/Servlet architecture to a Vuex-driven stack.}
            \resumeItem{Refactored UI architecture from JSP/Servlet pages to a Vuex-centric front-end model.}
            \resumeItem{Standardized state management for key business modules.}
            \resumeItem{Maintained compatibility with existing Java backend integrations.}
            \resumeItem{At HANBIRO VIETNAM, this migration reduced maintenance complexity for legacy UI layers and enabled faster feature iteration with a more consistent user experience.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Hanbiro Groupware: Business Management Website} $|$ \emph{Senior Fullstack Developer}}{}
          \resumeItemListStart
            \resumeItem{An enterprise groupware platform for internal operations, workflow management, and cross-department collaboration.}
            \resumeItem{Implemented internal workflow and business-management modules.}
            \resumeItem{Integrated multi-service backend with Golang/PHP and Angularjs/Reactjs front-end layers.}
            \resumeItem{Improved MySQL data query performance for high-usage operations.}
            \resumeItem{At HANBIRO VIETNAM, the platform standardized internal business workflows and improved operational collaboration across multiple departments.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Hanbiro HR: Timekeeping, Holiday, and Payroll Management (Web/App)} $|$ \emph{Senior Fullstack Developer}}{}
          \resumeItemListStart
            \resumeItem{An HR platform for timekeeping, leave management, and payroll operations across web and mobile applications.}
            \resumeItem{Designed flexible payroll and attendance modules for HR operations.}
            \resumeItem{Built React-Native mobile flows synchronized with web admin data.}
            \resumeItem{Structured Laravel APIs and MySQL data flows for daily HR workflows.}
            \resumeItem{At HANBIRO VIETNAM, this product automated core HR operations, reduced manual overhead, and improved transparency in people-operation data.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Hanbiro CRM: Supply Chain Management} $|$ \emph{Leader Fullstack Developer}}{}
          \resumeItemListStart
            \resumeItem{A CRM platform for supply-chain management, order tracking, and operational data coordination across business units.}
            \resumeItem{Designed a scalable CRM architecture for supply-chain workflows.}
            \resumeItem{Integrated GraphQL and Reactjs to optimize context-based data retrieval.}
            \resumeItem{Built high-throughput services with Golang and MySQL.}
            \resumeItem{At HANBIRO VIETNAM, this system improved supply-chain visibility, reduced cross-team information bottlenecks, and supported stronger operational decision-making.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Learning Chinese for Japanese} $|$ \emph{Fullstack Developer}}{}
          \resumeItemListStart
            \resumeItem{A mobile learning application helping Japanese users improve Chinese through interactive lessons, structured exercises, and progress-oriented practice journeys.}
            \resumeItem{Developed cross-platform mobile views using React-Native}
            \resumeItem{Integrated interactive language exercises backed by a .NET Core API}
            \resumeItem{Contributed to content delivery flow and user progression tracking for repeat learning usage.}
            \resumeItem{At FPT SOFTWARE, this app delivered a focused language-learning experience for a niche audience and maintained strong recurring usage through interactive lessons. The project validated mobile-first education delivery for international learners and supported product positioning in a specialized language market.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Medical Information Management} $|$ \emph{Fullstack Developer}}{}
          \resumeItemListStart
            \resumeItem{A healthcare mobile application enabling users to book appointments, manage reminders, and receive follow-up notifications with clinically relevant timing.}
            \resumeItem{Architected a secure backend to manage sensitive user medical records}
            \resumeItem{Implemented real-time push notifications for patient scheduling}
            \resumeItem{Supported patient workflow consistency through service-side validation and reminder orchestration.}
            \resumeItem{At FPT SOFTWARE, this product streamlined appointment workflows and prescription reminders for clinic users. It reduced missed bookings, improved patient follow-up consistency, and helped clinics coordinate more predictable daily appointment operations.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Riolish Mobile App} $|$ \emph{Team Leader}}{}
          \resumeItemListStart
            \resumeItem{An integrated admin web and mobile learning platform supporting English teaching operations, learner engagement, and content delivery for Vietnamese users.}
            \resumeItem{Developed a robust API for content delivery}
            \resumeItem{Built cross-platform mobile learning experiences}
            \resumeItem{Supported role-based administration flows for content, user, and course management.}
            \resumeItem{At VINHDANH COMPANY, Riolish created a scalable digital learning channel combining admin web and mobile learning flows. The platform improved learner retention, expanded service delivery for Vietnamese users, and enabled more structured operations for education teams.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Toshiba's Book Reading App} $|$ \emph{Internship Fullstack Developer}}{}
          \resumeItemListStart
            \resumeItem{Collaborated on the analysis and implementation of a digital reading application for Toshiba, focusing on document flow, readability, and stable user interaction.}
            \resumeItem{Contributed to software requirement analysis using StartUML}
            \resumeItem{Collaborated closely with cross-functional teams to design document rendering flows}
            \resumeItem{Supported quality assurance preparation through documentation and requirement alignment activities.}
            \resumeItem{At FPT SOFTWARE (internship phase), this project contributed to delivering a stable and user-friendly digital reading experience aligned with Toshiba's product quality expectations. It also provided early exposure to enterprise delivery standards and cross-functional collaboration practices.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Datasa E-Commerce Platform} $|$ \emph{Fullstack Developer}}{}
          \resumeItemListStart
            \resumeItem{A complete e-commerce platform for computer and mobile products, including customer storefront flows and an administrative portal for catalog and operations management.}
            \resumeItem{Developed dynamic product catalogs and secure checkout flows using ASP.NET MVC}
            \resumeItem{Designed a comprehensive relational database schema in Microsoft SQL}
            \resumeItem{Implemented order and product management workflows for day-to-day business operations.}
            \resumeItem{At DATASA.NET, this project established an operational e-commerce sales channel with both storefront and admin capabilities. It improved product management efficiency, simplified operational control for admins, and enabled sustainable online revenue growth.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Backend}{: .NET Core, ASP.NET Core, Java, Spring Boot, PHP, Laravel, Node.js} \\
     \textbf{Frontend}{: ReactJS, Vue.js, TypeScript, JavaScript, HTML5, CSS3, Angular} \\
     \textbf{Mobile}{: React Native, Android, iOS Basics} \\
     \textbf{Database}{: MySQL, PostgreSQL, Microsoft SQL Server, SQLite, MongoDB, Redis} \\
     \textbf{Messaging}{: Kafka, RabbitMQ} \\
     \textbf{Monitoring}{: Grafana, Prometheus, OpenTelemetry}
    }}
 \end{itemize}

\end{document}
